---
author: Matthew Swartwout
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: pdf_document
params:
    data_dir: '/home/matt/thesis/experiment_data'
    experiment: 'one_mobile'
    robot: '1'
title: '`r paste(params$experiment, "Turtlebot", params$robot, "Report")`'
---

```{r, echo=FALSE}
knitr::read_chunk('one_robot.R')
```

```{r, read_data, echo=FALSE}
```
```{r, calculations, echo=FALSE}
```
```{r, time, echo=FALSE}
```
This is a summary of the data from the `r params$experiment` experiment, Turtlebot #`r params$robot`.

The runtime of this experiment was `r partial_time_hours` hours, `r partial_time_minutes` minutes, and `r partial_time_seconds` seconds.

The total number of external pose measurements recieved by the robot during this time was `r external_poses` which means poses were received at an average of `r external_poses / total_time_seconds` poses per second.

Shown below is the summary of each filter's error for both x and y coordinates, and also the error in total distance.

```{r, summary}
```

<!-- Shown below are plots representing the robot's motion and error over time.

{r, plot, echo=FALSE}
-->


